Causal inference is not a statistical problem

### 2023-04-14 manuscript.qmd

# set default theme
theme_set(
  theme_minimal(
    base_size = 14, 
    base_family = "sans"
  ) %+replace% 
    theme(
      panel.grid.minor = element_blank(),
      legend.position = "bottom"
    )
)
theme_dag <- function() {
  ggdag::theme_dag(base_family = "sans")
}
geom_dag_label_repel <- function(..., seed = 10) {
  ggdag::geom_dag_label_repel(
    aes(x, y, label = label),
    box.padding = 3.5, 
    inherit.aes = FALSE,
    max.overlaps = Inf, 
    family = "sans",
    seed = seed,
    label.size = NA, 
    label.padding = 0.1,
    size = 14 / 3,
    ...
  ) 
}

```

@@

```{r}
#| label: fig-3
#| fig-cap: "Time-ordered collider DAG where each factor is measured twice. $X$ is the exposure, $Y$ is the outcome, and $Z$ is the measured factor. The highlighted $Z$ node indicates which time point is being adjusted for when estimating the average treatment effect of the highlighted $X$ on the highlighted $Y$"
#| fig-subcap: 
#|   - "Adjusting for $Z$ as shown here would induce collider bias."
#|   - "Adjusting for this pre-exposure $Z$ as shown here would **not** induce collider bias."
#| layout-ncol: 2
coords <- list(
  x = c(X_0 = 1, X_1 = 2, Z_1 = 2, Y_1 = 1.9, X_2 = 3, Y_2 = 2.9, Z_2 = 3,
        X_3 = 4, Y_3 = 3.9, Z_3 = 4),
  y = c(X_0 = 1, Y_0 = 1.05,
        X_1 = 1, Z_1 = 1.1, Y_1 = 1.05,
        X_2 = 1, Z_2 = 1.1, Y_2 = 1.05,
        X_3 = 1, Z_3 = 1.1, Y_3 = 1.05)
)
d_coll <- dagify(
  Y_2 ~ X_1,
  Y_3 ~ X_2,
  X_2 ~ X_1,
  Z_2 ~ X_1 + Y_2,
  Z_3 ~ X_2 + Y_3 + Z_2,
  exposure = "X_2",
  outcome = "Y_3",
  labels = c(X_0 = "X",
             X_1 = "X",
             X_2 = "X",
             X_3 = "X",
             Y_0 = "Y",
             Y_1 = "Y",
             Y_2 = "Y",
             Y_3 = "Y",
             Z_1 = "Z",
             Z_2 = "Z",
             Z_3 = "Z"),
  coords = coords
)

d_coll |>
  tidy_dagitty() |>
  mutate(color = case_when(
    !(name %in% c("X_2", "Y_3", "Z_3")) ~ "grey",
    TRUE ~ label)) |>
  ggplot(
    aes(x = x, y = y, xend = xend, yend = yend)
  ) +
  geom_dag_point(aes(color = color)) +
  geom_dag_edges() +
  geom_dag_text(aes(label = label)) +
  theme_dag() +
  coord_cartesian(clip = "off")  +
  scale_color_manual(values = c("lightgrey", "#A8CF9E", "#51c1ad", "#357edd")) +
  theme(legend.position = "none") + 
  geom_vline(xintercept = c(2.6, 3.25, 3.6, 4.25), lty = 2) + 
  annotate("label", x = 2.925, y = 0.97, label = "baseline") + 
  annotate("label", x = 3.925, y = 0.97, label = "follow-up")

d_coll |>
  tidy_dagitty() |>
  mutate(color = case_when(
    !(name %in% c("X_2", "Y_3", "Z_2")) ~ "grey",
    TRUE ~ label)) |>
  ggplot(
    aes(x = x, y = y, xend = xend, yend = yend)
  ) +
  geom_dag_point(aes(color = color)) +
  geom_dag_edges() +
  geom_dag_text(aes(label = label)) +
  theme_dag() +
  coord_cartesian(clip = "off")  +
  scale_color_manual(values = c("lightgrey", "#A8CF9E", "#51c1ad", "#357edd")) +
  theme(legend.position = "none") + 
  geom_vline(xintercept = c(2.6, 3.25, 3.6, 4.25), lty = 2) + 
  annotate("label", x = 2.925, y = 0.97, label = "baseline") + 
  annotate("label", x = 3.925, y = 0.97, label = "follow-up")
```

@@

causal_quartet_time |>
  nest_by(dataset) |>
  mutate(
    `ATE not adjusting for Z` = 
      round_coefs(lm(outcome_followup ~ exposure_baseline, data = data)),
    `ATE adjusting for Z` = 
      round_coefs(lm(
        outcome_followup ~ exposure_baseline + covariate_baseline, 
        data = data
      ))
  ) |>
  bind_cols(tibble(truth = c(1, 0.5, 1, 1))) |>
  select(-data, dataset) |>
  knitr::kable(
    "latex", 
    booktabs = TRUE,
    escape = FALSE, 
    col.names = kableExtra::linebreak(c(
      "Data generating mechanism", 
      "ATE\nnot adjusting for\npre-exposure Z", 
      "ATE\nadjusting for\npre-exposure Z",
      "Correct causal effect"), align = "c"),
    digits = 2
  ) 
```

>>>>

# set default theme
theme_set(
  theme_minimal(
    base_size = 14,
    base_family = "sans"
  ) %+replace%
    theme(
      panel.grid.minor = element_blank(),
      legend.position = "bottom"
    )
)
theme_dag <- function() {
  ggdag::theme_dag(base_family = "sans")
}
geom_dag_label_repel <- function(..., seed = 10) {
  ggdag::geom_dag_label_repel(
    aes(x, y, label = label),
    box.padding = 3.5,
    inherit.aes = FALSE,
    max.overlaps = Inf,
    family = "sans",
    seed = seed,
    label.size = NA,
    label.padding = 0.1,
    size = 14 / 3,
    ...
  )
}
```

@@

```{r}
#| label: fig-3
#| fig-cap: "Time-ordered collider DAG where each factor is measured twice. $X$ is the exposure, $Y$ is the outcome, and $Z$ is the measured factor. The highlighted $Z$ node indicates which time point is being adjusted for when estimating the average treatment effect of the highlighted $X$ on the highlighted $Y$"
#| fig-subcap:
#|   - "Adjusting for $Z$ as shown here would induce collider bias."
#|   - "Adjusting for this pre-exposure $Z$ as shown here would **not** induce collider bias."
#| layout-ncol: 2
coords <- list(
  x = c(
    X_0 = 1, X_1 = 2, Z_1 = 2, Y_1 = 1.9, X_2 = 3, Y_2 = 2.9, Z_2 = 3,
    X_3 = 4, Y_3 = 3.9, Z_3 = 4
  ),
  y = c(
    X_0 = 1, Y_0 = 1.05,
    X_1 = 1, Z_1 = 1.1, Y_1 = 1.05,
    X_2 = 1, Z_2 = 1.1, Y_2 = 1.05,
    X_3 = 1, Z_3 = 1.1, Y_3 = 1.05
  )
)
d_coll <- dagify(
  Y_2 ~ X_1,
  Y_3 ~ X_2,
  X_2 ~ X_1,
  Z_2 ~ X_1 + Y_2,
  Z_3 ~ X_2 + Y_3 + Z_2,
  exposure = "X_2",
  outcome = "Y_3",
  labels = c(
    X_0 = "X",
    X_1 = "X",
    X_2 = "X",
    X_3 = "X",
    Y_0 = "Y",
    Y_1 = "Y",
    Y_2 = "Y",
    Y_3 = "Y",
    Z_1 = "Z",
    Z_2 = "Z",
    Z_3 = "Z"
  ),
  coords = coords
)

d_coll |>
  tidy_dagitty() |>
  mutate(color = case_when(
    !(name %in% c("X_2", "Y_3", "Z_3")) ~ "grey",
    TRUE ~ label
  )) |>
  ggplot(
    aes(x = x, y = y, xend = xend, yend = yend)
  ) +
  geom_dag_point(aes(color = color)) +
  geom_dag_edges() +
  geom_dag_text(aes(label = label)) +
  theme_dag() +
  coord_cartesian(clip = "off") +
  scale_color_manual(values = c("lightgrey", "#A8CF9E", "#51c1ad", "#357edd")) +
  theme(legend.position = "none") +
  geom_vline(xintercept = c(2.6, 3.25, 3.6, 4.25), lty = 2) +
  annotate("label", x = 2.925, y = 0.97, label = "baseline") +
  annotate("label", x = 3.925, y = 0.97, label = "follow-up")

d_coll |>
  tidy_dagitty() |>
  mutate(color = case_when(
    !(name %in% c("X_2", "Y_3", "Z_2")) ~ "grey",
    TRUE ~ label
  )) |>
  ggplot(
    aes(x = x, y = y, xend = xend, yend = yend)
  ) +
  geom_dag_point(aes(color = color)) +
  geom_dag_edges() +
  geom_dag_text(aes(label = label)) +
  theme_dag() +
  coord_cartesian(clip = "off") +
  scale_color_manual(values = c("lightgrey", "#A8CF9E", "#51c1ad", "#357edd")) +
  theme(legend.position = "none") +
  geom_vline(xintercept = c(2.6, 3.25, 3.6, 4.25), lty = 2) +
  annotate("label", x = 2.925, y = 0.97, label = "baseline") +
  annotate("label", x = 3.925, y = 0.97, label = "follow-up")
```

@@

causal_quartet_time |>
  nest_by(dataset) |>
  mutate(
    `ATE not adjusting for Z` =
      round_coefs(lm(outcome_followup ~ exposure_baseline, data = data)),
    `ATE adjusting for Z` =
      round_coefs(lm(
        outcome_followup ~ exposure_baseline + covariate_baseline,
        data = data
      ))
  ) |>
  bind_cols(tibble(truth = c(1, 0.5, 1, 1))) |>
  select(-data, dataset) |>
  knitr::kable(
    "latex",
    booktabs = TRUE,
    escape = FALSE,
    col.names = kableExtra::linebreak(c(
      "Data generating mechanism",
      "ATE\nnot adjusting for\npre-exposure Z",
      "ATE\nadjusting for\npre-exposure Z",
      "Correct causal effect"
    ), align = "c"),
    digits = 2
  )
```

### 2023-04-14 manuscript.tex

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, interior hidden, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\FunctionTok{ggplot}\NormalTok{(causal\_quartet, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ exposure, }\AttributeTok{y =}\NormalTok{ outcome)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.25}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{geom\_smooth}\NormalTok{(}
    \AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }
    \AttributeTok{formula =} \StringTok{"y \textasciitilde{} x"}\NormalTok{, }
    \AttributeTok{linewidth =} \FloatTok{1.1}\NormalTok{, }
    \AttributeTok{color =} \StringTok{"steelblue"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{dataset)}
\DocumentationTok{\#\# Table 2}
\NormalTok{round\_coefs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(.mdl) \{}
  \FunctionTok{round}\NormalTok{(}\FunctionTok{coef}\NormalTok{(.mdl)[}\DecValTok{2}\NormalTok{], }\DecValTok{2}\NormalTok{)}
\NormalTok{\}}

\NormalTok{causal\_quartet }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{nest\_by}\NormalTok{(dataset) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE not adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure }\SpecialCharTok{+}\NormalTok{ covariate, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{Correlation of X and Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round}\NormalTok{(}\FunctionTok{cor}\NormalTok{(data}\SpecialCharTok{$}\NormalTok{exposure, data}\SpecialCharTok{$}\NormalTok{covariate), }\DecValTok{2}\NormalTok{)}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{data, dataset) }\SpecialCharTok{|\textgreater{}}
\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
    \StringTok{"latex"}\NormalTok{, }
    \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{, }
    \AttributeTok{col.names =}\NormalTok{ kableExtra}\SpecialCharTok{::}\FunctionTok{linebreak}\NormalTok{(}\FunctionTok{c}\NormalTok{(}
      \StringTok{"Data generating mechanism"}\NormalTok{, }
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{not adjusting for Z"}\NormalTok{, }
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{adjusting for Z"}\NormalTok{, }
      \StringTok{"Correlation of}\SpecialCharTok{\textbackslash{}n}\StringTok{X and Z"}
\NormalTok{      ), }\AttributeTok{align =} \StringTok{"c"}\NormalTok{)}
\NormalTok{  ) }
\DocumentationTok{\#\# Table 3}

\NormalTok{causal\_quartet\_time }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{nest\_by}\NormalTok{(dataset) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE not adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} 
      \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome\_followup }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure\_baseline, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} 
      \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(}
\NormalTok{        outcome\_followup }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure\_baseline }\SpecialCharTok{+}\NormalTok{ covariate\_baseline, }
        \AttributeTok{data =}\NormalTok{ data}
\NormalTok{      ))}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{tibble}\NormalTok{(}\AttributeTok{truth =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{data, dataset) }\SpecialCharTok{|\textgreater{}}
\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
    \StringTok{"latex"}\NormalTok{, }
    \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{, }
    \AttributeTok{col.names =}\NormalTok{ kableExtra}\SpecialCharTok{::}\FunctionTok{linebreak}\NormalTok{(}\FunctionTok{c}\NormalTok{(}
      \StringTok{"Data generating mechanism"}\NormalTok{, }
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{not adjusting for}\SpecialCharTok{\textbackslash{}n}\StringTok{pre{-}exposure Z"}\NormalTok{, }
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{adjusting for}\SpecialCharTok{\textbackslash{}n}\StringTok{pre{-}exposure Z"}\NormalTok{,}
      \StringTok{"Correct causal effect"}\NormalTok{), }\AttributeTok{align =} \StringTok{"c"}\NormalTok{),}
    \AttributeTok{digits =} \DecValTok{2}
\NormalTok{  ) }
\end{Highlighting}
\end{Shaded}

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden]}{\end{tcolorbox}}\fi

@@

\FunctionTok{ggplot}\NormalTok{(causal\_quartet, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ exposure, }\AttributeTok{y =}\NormalTok{ outcome)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.25}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_smooth}\NormalTok{(}
    \AttributeTok{method =} \StringTok{"lm"}\NormalTok{,}
    \AttributeTok{formula =} \StringTok{"y \textasciitilde{} x"}\NormalTok{,}
    \AttributeTok{linewidth =} \FloatTok{1.1}\NormalTok{,}
    \AttributeTok{color =} \StringTok{"steelblue"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{dataset)}
\DocumentationTok{\#\# Table 2}
\NormalTok{round\_coefs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(.mdl) \{}
  \FunctionTok{round}\NormalTok{(}\FunctionTok{coef}\NormalTok{(.mdl)[}\DecValTok{2}\NormalTok{], }\DecValTok{2}\NormalTok{)}
\NormalTok{\}}

\NormalTok{causal\_quartet }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{nest\_by}\NormalTok{(dataset) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE not adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure }\SpecialCharTok{+}\NormalTok{ covariate, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{Correlation of X and Z}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{round}\NormalTok{(}\FunctionTok{cor}\NormalTok{(data}\SpecialCharTok{$}\NormalTok{exposure, data}\SpecialCharTok{$}\NormalTok{covariate), }\DecValTok{2}\NormalTok{)}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{data, dataset) }\SpecialCharTok{|\textgreater{}}
\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
    \StringTok{"latex"}\NormalTok{,}
    \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{,}
    \AttributeTok{col.names =}\NormalTok{ kableExtra}\SpecialCharTok{::}\FunctionTok{linebreak}\NormalTok{(}\FunctionTok{c}\NormalTok{(}
      \StringTok{"Data generating mechanism"}\NormalTok{,}
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{not adjusting for Z"}\NormalTok{,}
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{adjusting for Z"}\NormalTok{,}
      \StringTok{"Correlation of}\SpecialCharTok{\textbackslash{}n}\StringTok{X and Z"}
\NormalTok{    ), }\AttributeTok{align =} \StringTok{"c"}\NormalTok{)}
\NormalTok{  )}
\DocumentationTok{\#\# Table 3}

\NormalTok{causal\_quartet\_time }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{nest\_by}\NormalTok{(dataset) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE not adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=}
      \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(outcome\_followup }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure\_baseline, }\AttributeTok{data =}\NormalTok{ data)),}
    \StringTok{\textasciigrave{}}\AttributeTok{ATE adjusting for Z}\StringTok{\textasciigrave{}} \OtherTok{=}
      \FunctionTok{round\_coefs}\NormalTok{(}\FunctionTok{lm}\NormalTok{(}
\NormalTok{        outcome\_followup }\SpecialCharTok{\textasciitilde{}}\NormalTok{ exposure\_baseline }\SpecialCharTok{+}\NormalTok{ covariate\_baseline,}
        \AttributeTok{data =}\NormalTok{ data}
\NormalTok{      ))}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{tibble}\NormalTok{(}\AttributeTok{truth =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{data, dataset) }\SpecialCharTok{|\textgreater{}}
\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
    \StringTok{"latex"}\NormalTok{,}
    \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{,}
    \AttributeTok{col.names =}\NormalTok{ kableExtra}\SpecialCharTok{::}\FunctionTok{linebreak}\NormalTok{(}\FunctionTok{c}\NormalTok{(}
      \StringTok{"Data generating mechanism"}\NormalTok{,}
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{not adjusting for}\SpecialCharTok{\textbackslash{}n}\StringTok{pre{-}exposure Z"}\NormalTok{,}
      \StringTok{"ATE}\SpecialCharTok{\textbackslash{}n}\StringTok{adjusting for}\SpecialCharTok{\textbackslash{}n}\StringTok{pre{-}exposure Z"}\NormalTok{,}
      \StringTok{"Correct causal effect"}
\NormalTok{    ), }\AttributeTok{align =} \StringTok{"c"}\NormalTok{),}
    \AttributeTok{digits =} \DecValTok{2}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}
